Analysing the three-dimensional structure of \em{P. falciparum}

### 2017-07-03 doc/manuscript/paper.tex
Wish distances

A crucial step of MDS-based method rely on finding a good set of
``wish-distances'' from Hi-C contact count data.

@@

Note that in practice, the constraints are mostly intrinsic to the data and
thus can be dropped.

@@

\subsubsection{Modeling contact counts as a Negative Binomial distribution}

@@

>>>>

A crucial step of MDS-based method rely on finding a good set of
``wish-distances'' from Hi-C contact count data. While several approach have
been used in the litterature, most leverage bio-physics relationships either
between the genomic distnaces $s$ and the expected count, or the relationship
between the euclidean distance $d$ and the expected
count. \citet{ay:three-dimensional} observe that {\em P. falciparum}'s DNA
behave like a fractal globule polymer. \citet{grosberg:fractal} show fractal
globul polymer exhibits a well-defined relationship between its genomic length
and physical distance $d$:

$$d\sim s^{1/3}$$

The relationship between genomic distance $s$ and $c$ can be derived from the
data, by fitting a linear model between the log expected count and the genomic
distances.

@@

Note that in practice, the constraints are fulfilled naturally by the data,
and thus can be dropped.

@@

@@

In order to integrate
